Copulas and their potential for ecology

### 2019-06-12 Paper.Rmd
starting revisions post Ecol Lett

---
title: "Copulas reveal complex and informative dependencies propagating throughout ecology"
author: "Shyamolina Ghosh, Lawrence W. Sheppard, Mark T. Holder, Terrance E. Loecke, Philip C. Reid, James D. Bever, Daniel C. Reuman"
date: ""
geometry: "left=1.5cm,right=1.5cm,top=2.5cm,bottom=2.8cm"

@@

# Front matter

@@

\noindent Ghosh: Department of Ecology and Evolutionary Biology and Kansas Biological Survey, University of Kansas, Lawrence, KS, 66045, USA

\noindent Sheppard: Department of Ecology and Evolutionary Biology and Kansas Biological Survey, University of Kansas, Lawrence, KS, 66045, USA

@@

\noindent Bever: Department of Ecology and Evolutionary Biology and Kansas Biological Survey, University of Kansas, Lawrence, KS, 66045, USA

@@

@@

Copulas and their potential for ecology

@@

\noindent \emph{Type of Article:} Ideas and Perspectives

\noindent \emph{The number of words in the abstract:} 250

\noindent \emph{The number of words in the main text (excluding abstract, acknowledgements, references, table and figure legends):} 7497

\noindent \emph{The number of words in each text box:} No text boxes

\noindent \emph{The number of references:} 34

\noindent \emph{The number of figures, tables, and text boxes:} 7 figures, 3 tables, 0 text boxes

\noindent \emph{The name and complete mailing address (including telephone and fax numbers and e-mail address) of the person to whom correspondence should be sent:} Daniel Reuman, 2101 Constant Ave, Lawrence, KS, 66047, reuman@ku.edu, 626 560 7084.

\newpage

@@

\newpage
# Introduction\label{Intro}

>>>>

---
title: "Copulas and their potential for ecology"
author: "Shyamolina Ghosh, Lawrence W. Sheppard, Mark T. Holder, Terrance E. Loecke, Philip C. Reid, James D. Bever, Daniel C. Reuman"
date: ""
fontsize: 12pt
geometry: "left=2.54cm,right=2.54cm,top=2.54cm,bottom=2.54cm"

@@

@@

\noindent Ghosh, Sheppard, Bever: Department of Ecology and Evolutionary Biology and Kansas Biological Survey, University of Kansas, Lawrence, KS, 66045, USA

@@

@@

Copulas reveal complex and informative dependencies propagating throughout ecology

@@

@@

\noindent \emph{Correspondence:} Daniel Reuman, 2101 Constant Ave, Lawrence, KS, 66047, reuman@ku.edu, 626 560 7084.

\noindent \emph{Type of Submission:} Article

\noindent \emph{The number of words in the abstract:}

@@

# Introduction\label{Intro}
